Data Management for LSST Special Programs

### 2023-10-18 sec_sci.tex
move details to sec:proc

There are three main reasons for this recommendation.

@@

\textbf{Special Processing should be done by Rubin Data Management to 
produce unique and separate (but joinable) data products
for Special Programs when it is both possible and necessary.}

@@

There are two main reasons for this recommendation.

@@

Specific examples are provided only to illustrate this recommendation.
These examples do not place limits on what Special Processing might be done.

\begin{itemize}

\item \textbf{Possible and necessary:}
in order to detect high-redshift (faint) galaxies in the DDFs,
Rubin Data Management uses the LSST Science Pipelines to deeply
coadd images for each field, and store the results of source
detection and characterization in unique and separate tables that
are included in the annual data release (Section~\ref{ssec:proc_rdm_ddf}).

\item \textbf{Possible but not necessary:}
a time-domain mini-survey that uses standard visits \emph{could}
have separate difference-image analysis object and source catalogs
generated, but this is not necessary as the science goals for the
mini-survey can be met by processing its data with regular Prompt
Processing (Section~\ref{ssec:sci_pproc}), and ensuring the
data is properly labeled (Section~\ref{ssec:sci_labels}).

\item \textbf{Possible but not necessary (secondary science goals):}
a time-domain mini-survey (or DDF) has a secondary science goal of detecting
precursor outbursts for transients, which requires coadding images
within windows of days, weeks, and months to reach various depths.
This set of custom coadds may be considered as ``not necessary" and requiring 
User-Generated Processing.

\item \textbf{Necessary but not possible:}
in order to find the most distant, faint Kuiper Belt Objects in the DDF,
a specialized, computationally intensive form of ``shift-and-stack" processing
is required for detection, but such algorithms are not used by the 
LSST Science Pipelines and so User-Generated Processing will be needed (Section~\ref{ssec:SPCS_TNO}).
A second example here is a twilight survey that uses non-standard visits 
which are outside the boundaries of what the LSST
Science Pipelines can process (Section~\ref{ssec:proc_bounds}).

\end{itemize}

@@

The phrase ``can be processed" includes all standard and alternative visits in 
sky regions for which a template image exists.
This might also include some non-standard visits (shorter or longer exposures), 
as long as they can be processed by the Prompt pipeline and an appropriate template image exists.

Visits with very short or very long exposure times (or very bright sky 
backgrounds) might be excluded if they would need specialized algorithms for,
e.g., instrument signature removal, difference-imaging, template-generation 
(Section~\ref{ssec:proc_bounds}).

If a Special Program's primary science goal requires specialized templates and 
Prompt processing, the Data Management System will have the capability to load 
and use an alternative template for some sky regions, based on the image metadata 
(i.e., the labels described in Section~\ref{ssec:sci_labels}). 
However, there would not be enough memory to hold alternative templates 
for the whole sky.

Including visits from Special Programs in regular Prompt processing alongside
vists from the WFD program is not, in general, anticipated to affect WFD science goals.
For example, analyses for a WFD-only subset could still be done using the program and
region labels described in Section~\ref{ssec:sci_labels}.
However, a few concerns are raised in Section~\ref{ssec:proc_prompt}.

>>>>

There are three main motivations for this recommendation.

@@

\textbf{Special Processing should be done by Rubin Data Management to 
produce unique and separate data products
for Special Programs when it is both possible and necessary.}

@@

There are two main motivations for this recommendation.

@@

Further discussion on Special Processing, with examples, is provided in Section~\ref{ssec:proc_special}.

@@

The condition ``can be processed" is ultimately left to the discretion of
Rubin Data Management in Rubin Operations, but it is expected to include
all standard and alternative visits in sky regions for which a template image exists.

The main motivation for this recommendation is that all time-domain and 
moving-object science goals (two of the four science pillars for the LSST) are
enhanced by any and all additional observations, even if they are not
optimized for the science (as the WFD program's cadence is being optimized).

Further discussion of regular Prompt processing of Special Programs data, with
examples and a discussion of a few challenges,
is provided in Section~\ref{ssec:proc_reg_prompt}.
